---
title: "CESAB training - Quarto"
format: html
editor: visual
execute: 
  echo: false
  message: false
---

## Packages

We load the `tidyverse`package.

```{r,echo=FALSE,message=FALSE}
library(tidyverse,quietly = TRUE)
```

## Importing data

We load the .csv files using the `import_wwf()` function.

```{r,echo=FALSE,message=FALSE}
#source(here::here("R","import_wwf.R"))
#import_wwf()
```

## Select Ursidae family

We are interested in the Ursidae family only so we filtered data.

```{r,echo=FALSE,message=FALSE}
#source(here::here("R","select_family.R"))
#ursidae <- select_family(mammals,"Ursidae")
```

## Join tables

We create a table containing informations about species and details about their associated ecoregions.

```{r,echo=FALSE,message=FALSE}
#source(here::here("R","join_table.R"))
# data <- join_table(ursidae,
#                    ecoregion, 
#                    asso)
```

## Count number of ecoregions

We count the number of ecoregions where a species can be found

```{r,echo=FALSE,message=FALSE}
# source(here::here("R","count_ecoregion.R"))
# count <- count_ecoregion(data)
# knitr::kable(count)
targets::tar_load(count_data)
knitr::kable(count_data)
```

## Graphical representation

We represent

```{r,echo=FALSE,message=FALSE}
#| label: barplot
#| fig-cap: "Number of ecoregions per species"
# source(here::here("R","plot_ecoregion_species.R"))
# p <- plot_ecoregion_species(count)
# print(p)
targets::tar_load(barplot)
print(barplot)
```
